Intelligent Quadcopter for IARC 2018

### 2018-06-01 IARC_Paper_2018/Paper.tex
Marks changes

		\subsection*{Target Identification}
			For target identification, the drone carries five Logitech C270 USB webcams. One of the cameras is located at the bottom of the drone and faces straight downward. The other four cameras are mounted on the bottom side of each arm facing outward. All five cameras are mounted for identifying as many target Roombas surrounding the drone as possible in order to send their coordinates to the strategy node.

@@

				Pixel given from YOLO: $PIX$ Pixel number of the center:

				\begin{center}
					$PIX = \frac{PIX\_MAX}{2}$
				\end{center}

				Define $\phi$ as portion of angle from center image to pixel detected:

				\begin{center}
					$\phi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})$
				\end{center}

@@

						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$, Then:
						\begin{center}
							$REAL = z * tan(\theta + \frac{\phi}{2})$
						\end{center}
						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$, Then:
						\begin{center}
							$REAL = z * tan(\theta - \frac{\phi}{2})$
						\end{center}
				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$
						\begin{center}
							$REAL = z * tan(\theta - \frac{\phi}{2})$
						\end{center}
						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$
						\begin{center}
							$REAL = z * tan(\theta + \frac{\phi}{2})$
						\end{center}
				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
			\end{spacing}

@@

>>>>

		\subsection*{Target Identification}
			For target identification, the drone carries four Logitech C270 USB webcams and one Logitech C210 USB webcam. One of the cameras is located at the bottom of the drone and faces straight downward. The other four cameras are mounted on the bottom side of each arm facing outward. All five cameras are mounted for identifying as many target Roombas surrounding the drone as possible in order to send their coordinates to the strategy node.

@@

				Pixel given from YOLO: $PIX$

				\begin{center}
					Pixel number of the center: $PIX\_CTR = \frac{PIX\_MAX}{2}$
				\end{center}

				Define $\psi$ as portion of angle from center image to pixel detected:

				\begin{center}
					$\psi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})$
				\end{center}

@@

						\tab If $PIX$ lies above the center pixel, that is $PIX > PIX\_CTR$, Then:
						\begin{center}
							$REAL = z * tan(\theta + \frac{\psi}{2})$
						\end{center}
						\tab If $PIX$ lies below the center pixel, that is $PIX < PIX\_CTR$, Then:
						\begin{center}
							$REAL = z * tan(\theta - \frac{\psi}{2})$
						\end{center}
				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
						\tab If $PIX$ lies above the center pixel, that is $PIX > PIX\_CTR$
						\begin{center}
							$REAL = z * tan(\theta - \frac{\psi}{2})$
						\end{center}
						\tab If $PIX$ lies below the center pixel, that is $PIX < PIX\_CTR$
						\begin{center}
							$REAL = z * tan(\theta + \frac{\psi}{2})$
						\end{center}
				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
			\end{spacing}

@@

		This is different from the x only because top of frame is $1$ and bottom is $PIX\_MAX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
